### 2016-08-03 hoist.tex
pessimistic approach

\section{Comparative analysis of different approaches to hoisting}
\subsection{Optimistic approach}
Collect GVN of all the instructions in the beginning.
\subsection{Pessimistic approach}
Start from a branch. Hoist one by one iteratively.
\subsection{Triangle approach}

@@

Essentially,
abs(DFS-in(I1) - DFS-in(I2)) < abs(DFS-in(I1) - DFS-in(I3))
=> dist(I1, nearest-common-dom(I1, I2)) <= dist(I1, nearest-common-dom(I1, I3))

This means for candidates closer to each other w.r.t. DFS numbers, we
would make fewer checks for preconditions.

We partition the list at the point where the above mentioned checks fail.

@@

\section{Improving the Inliner heuristics}
Reducing the number of instructions also reduces the inline cost and
hence improves the inliner heuristics.

>>>>

\section{Comparative analysis of different approaches to hoisting}
\subsection{Optimistic approach}
Collect GVN of all the instructions in the beginning.

\subsection{Triangle approach}
This is the most basic approach to code-hoisting when the instructions are
hoisted to immediate parent in a diamond like structure. When there are
identical computations in both the branches of a conditional, and all the
legality checks are met, the instruction can be hoisted to the predecessor basic
block. This approach is simple to implement and has minimal impact on the
register pressure.

\subsection{Pessimistic approach}
To extend the triangle approach to the entire function, the algorithm traverses
the basic blocks in the invers depth-first order. All the leaf nodes are visited
before the non-leaf nodes because instructions are hoisted upwards. We start
from a branch and collect the GVN of all the instructions. Then in the sibling
basic block we find if there are any identical computations. Once we find an
identical computation we try to hoist it to the nearest common dominator which
is the immediate predecessor of both the basic blocks. We traverse the basic
block from top to down so that the once an instruction is hoisted it creates
opportunities for other dependent instructions. After all the sibling basic
blocks have all the identical computations hoisted, we continue the hoisting
process with their parent and its sibling of their parent until we reach the
beginning of the function.

@@

Essentially,
abs(DFSIn(I1) - DFSIn(I2)) < abs(DFSIn(I1) - DFSIn(I3))
=> bbDist(I1, nearest-common-dom(I1, I2)) <= bbDist(I1, nearest-common-dom(I1, I3))

This means for candidates closer to each other w.r.t. DFS numbers:
\begin{enumerate}
\item would make fewer checks for preconditions.
\item hoisting point will be closer so, the intersection of live-range of the instruction
with other instructions will be minimal.
\end{enumerate}

In our current implementation we partition the list at the point where the
legality/profitability checks fail.

@@

\section{Improving the Inliner heuristics}
Reducing the number of instructions also reduces the inlining cost and
hence improves the inliner heuristics.
